Poseidon Adventure

### 2023-05-17 NewCatchWorkflow.Rmd
test with NOBA sacc30-climate run

---
title: "New catch functions from CATCH.nc file"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), ''%d %B %Y'')`"
output: html_document
---

@@

Here is the new script, tested with snippets in mskeyrun sarah_wgsamsim branch and implemented in atlantisom dev branch

@@

```

### Test `load_nc_catchtons` with the NOBA, NEUS, CC model outputs

```

>>>>

---
title: "New catch functions from CATCH.nc file"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_fold: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(here)
library(stringr)
library(magrittr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(atlantisom)
```

@@

Here is the new function, tested with snippets in mskeyrun sarah_wgsamsim branch and implemented in atlantisom dev branch

```{r, code = readLines("https://raw.githubusercontent.com/r4atlantis/atlantisom/dev/R/load_nc_catchtons.R"), eval=F}
```

### 2. Test `load_nc_catchtons` with the NOBA, NEUS, CC model outputs

Only NOBA first, this one sacc30 with climate, different from sacc38 in mskeyrun without

@@

# define for each model

## NOBA (different from mskeyrun version)

atlmod <- here("config/NOBAsacc30Config.R")

select_groups <- c("Long_rough_dab",
                   "Green_halibut",
                   "Mackerel",
                   "Haddock",
                   "Saithe",
                   "Redfish",
                   "Blue_whiting",
                   "Norwegian_ssh",
                   "North_atl_cod",
                   "Polar_cod",
                   "Capelin")

stepperyr <- 5

## CC

## NEUS

##### aggregate over polygons to fleets #######
# make this a function

source(atlmod)

dir <- d.name
nc_catch <- paste0(scenario.name, 'CATCH.nc')
file_fgs <- functional.groups.file
file_init <- initial.conditions.file
file_fish <- fisheries.file

# Get the boundary boxes
allboxes <- atlantisom::load_box(dir = d.name, file_bgm = box.file)
boxes <- atlantisom::get_boundary(allboxes)

  # Read in information
  # Read in the functional groups csv since that is used by many functions
  fgs <- load_fgs(dir = dir, file_fgs = file_fgs)
  # Read in the biomass pools
  bps <- load_bps(dir = dir, fgs = file_fgs, file_init = file_init)

  catchtons <- load_nc_catchtons(dir = dir,
                                 file_nc = nc_catch,
                                 file_fish = file_fish,
                                 bps = bps,
                                 fgs = fgs,
                                 select_groups = select_groups,
                                 select_variable = "Catch",
                                 check_acronyms = TRUE,
                                 bboxes = boxes)
  #if(verbose) message("Catch tons read in.")

# result is output of load_nc_catchtons

aggcatchtons <- catchtons %>%
  dplyr::select(-agecl) %>%
  dplyr::group_by(species, fleet, time) %>%
  dplyr::summarise(totcatch = sum(atoutput)) %>%
  dplyr::mutate(year = ceiling(time/stepperyr))

# compare annual catch in tons to CATCH.txt output
yearcatchtons <- aggcatchtons %>%
  dplyr::group_by(species, year) %>%
  dplyr::summarise(yeartot = sum(totcatch))

txtCatchtons <- atlantisom::load_catch(d.name, catch.file, fgs) %>%
  dplyr::filter(species %in% select_groups) %>%
  dplyr::mutate(year = time/365) %>%
  dplyr::left_join(dplyr::select(fgs, Code, Name), by = c("species" = "Name"))

comparetons <- txtCatchtons %>%
  dplyr::left_join(yearcatchtons, by = c("Code" = "species", "year" = "year")) %>%
  ggplot2::ggplot() +
  geom_line(aes(year, atoutput)) +
  geom_point(aes(year, yeartot), color = "blue", alpha = 0.2) +
  facet_wrap(~species, scales="free_y")

# looks like a match!               
comparetons
```

### 2023-05-17 docs/index.Rmd
add new CC run
test with NOBA sacc30-climate run

>>>>

### New workflow testing for WGSAM simulated datasets

<a href="https://sgaichas.github.io/poseidon-dev/NewCatchWorkflow.html" target="_blank"> Total catch in tons now by polygon, fleet, and subannual timestep, in honor of Norwegian Constitution Day, May 17, 2023</a>

### New CCA run

<a href="https://sgaichas.github.io/poseidon-dev/NewCCASardines.html" target="_blank"> Test run from Isaac, June 30, 2022</a>
